\huge A Usability Evaluation of Tor Launcher

### 2017-03-20 pets2017-paper/pets2017-paper.tex
refer to users in plural for all three metrics
fix wrong word

\begin{itemize}
\item {\bfseries Completion rate:}  the percentage of users that want to connect to Tor and successfully do so. The higher the completion rate, the better. The ideal case would be that everyone is able to connect to Tor if they want to. Even if users do not successfully connect to Tor at first but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
\item {\bfseries Connection time:} the amount of time a user takes to connect to Tor. The less time it takes for users to connect, the better. The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to a couple minutes. Connection time includes this bootstrapping time and any additional time that people spend in the interface. 
\item {\bfseries Configuration time:} the amount of time users spend in the interface. The less time it takes for users to configure their preferences, the better. Configuration time is included in connection time, so it will always be less than connection time. We defined configuration time as any time spent on the bridge and proxy screens, since users were most likely configuring bridges and proxies. We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or timeout and not necessarily interacting with the interface. This should be as short as possible.
\end{itemize}

@@

\section{Qualitative Testing}
\label{sec:qualitative}
We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user. We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.

>>>>

\begin{itemize}
\item {\bfseries Completion rate:}  the percentage of users that want to connect to Tor and successfully do so. The higher the completion rate, the better. The ideal case would be that everyone is able to connect to Tor if they want to. Even if users do not successfully connect to Tor at first but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
\item {\bfseries Connection time:} the amount of time users take to connect to Tor. The less time it takes for users to connect, the better. The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to a couple minutes. Connection time includes this bootstrapping time and any additional time that people spend in the interface. 
\item {\bfseries Configuration time:} the amount of time users spend in the interface. The less time it takes for users to configure their preferences, the better. Configuration time is included in connection time, so it will always be less than connection time. We defined configuration time as any time spent on the bridge and proxy screens, since users were most likely configuring bridges and proxies. We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or timeout and not necessarily interacting with the interface. This should be as short as possible.
\end{itemize}

@@

\section{Qualitative Testing}
\label{sec:qualitative}
We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use. We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.
